Codes for Figure 4

### 2021-03-26 manuscript.Rmd
version for BMC bioinformatics

---
output: word_document
bibliography: /home/xiang/Documents/Bibliography/seahorse.bib
csl: scientific-reports.csl
---

@@

Mitochondrial dysfunction is involved in many complex diseases. 
Efficient and accurate evaluation of mitochondrial functionality is crucial for understanding pathology as well as facilitating novel therapeutic developments. 
As a popular platform, Seahorse extracellular flux (XF) analyzer is widely used for measuring mitochondrial oxygen consumption rate (OCR) in living cells. 
A hidden feature of Seahorse XF OCR data is that it has a complex data structure, caused by nesting and crossing between measurement cycles, wells and plates. 
Surprisingly, statistical analysis of Seahorse XF data has not received sufficient attention, and current methods completely ignore the complex data structure, impairing the robustness of statistical inference. 
To rigorously incorporate the complex structure into data analysis, here we developed a Bayesian hierarchical modeling framework, OCRbayes, and demonstrated its applicability based on analysis of published data sets. 
We showed that OCRbayes can analyze Seahorse XF OCR experimental data derived from either single or multiple plates. 
Moreover, OCRbayes has potential to be used for diagnosing patients with mitochondrial diseases.

@@

# Data Availability

The dataset supporting the conclusions of this article is included within the article and its additional file.

# Author contributions

@@

# Competing interests

>>>>

---
output: word_document
bibliography: /home/xiang/Documents/Bibliography/seahorse.bib
csl: bmc-bioinformatics.csl
---

@@

Background: Mitochondrial dysfunction is involved in many complex diseases. 
Efficient and accurate evaluation of mitochondrial functionality is crucial for understanding pathology as well as facilitating novel therapeutic developments. 
As a popular platform, Seahorse extracellular flux (XF) analyzer is widely used for measuring mitochondrial oxygen consumption rate (OCR) in living cells. 
A hidden feature of Seahorse XF OCR data is that it has a complex data structure, caused by nesting and crossing between measurement cycles, wells and plates. 
Surprisingly, statistical analysis of Seahorse XF data has not received sufficient attention, and current methods completely ignore the complex data structure, impairing the robustness of statistical inference.

Results: To rigorously incorporate the complex structure into data analysis, here we developed a Bayesian hierarchical modeling framework, OCRbayes, and demonstrated its applicability based on analysis of published data sets.

Conclusions: We showed that OCRbayes can analyze Seahorse XF OCR experimental data derived from either single or multiple plates. 
Moreover, OCRbayes has potential to be used for diagnosing patients with mitochondrial diseases.

Keywords: Oxygen consumption rate; mitochondria; Bayesian; hierarchical modeling; seahorse extracellular flux

@@

## Declarations

# Ethics approval and consent to participate

Not applicable

## Consent for publication

## Availability of data and materials

The datasets analysed during the current study are available in the Github repository, https://github.com/XiangZhangSC/seahorse.

## Competing interests

## Funding

Not applicable

## Author's contributions

@@

## Acknowledgements

Not applicable
